### 2021-06-24 Supplementary_Material/Regression_Trees_Subset_Nectar_Pollen.Rmd
edits

set.seed(2)
tree1 <- rpart(Visits~., data=v_df, cp=0.0134316) #6 splits is lower than the best tree plus on sd (rule of thumb for selecting trees)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459) #6node divisons it is within on sd + error of best tree

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) #7node divisons

par(mfrow=c(1,3))

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.15,type = 2) 
rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.15,type = 2)

>>>>

set.seed(2)
tree1 <- rpart(Visits~., data=v_df, cp=0.0154001)

set.seed(2)
tree2 <- rpart(`Normalized degree`~., data=nd_df, cp=0.0125459)

set.seed(2)
tree3 <- rpart(Specialization~., data=d_df, cp=0.0190352) 
par(mfrow=c(1,3))

rpart.plot(tree1, box.palette="GnOr", main="(a) Interaction frequency", cex.main=1.5,tweak = 1.25,type = 2) 
rpart.plot(tree2, box.palette="GnOr", main="(b) Normalized degree", cex.main=1.5,tweak = 1.25,type = 2)
rpart.plot(tree3, box.palette="GnOr", main="(c) Specialization", cex.main=1.5,tweak = 1.15,type = 2)
